Going from coarse landings data to fine scale species distribution

### 2022-05-06 Version_M2_plusieurszones/draft/paper_3/paper_3.Rmd
WIP

\begin{equation}
\label{eq:defY}
Y_i | S(x_i)  \overset{ind}{\sim} \M{p_i}{\mu_i}{\sigma^2}
\end{equation}
with $p_i \defeq \exp(-e^\xi S(x_{i})$ the proportion of the mixture, $\mu_i\defeq 
\frac{S(x_i)}{1-p_i}$ the expected catch when positive and $\sigma^2$ its variance (this parametrization of a lognormal distribution is detailed in SMXXXX and corresponds to

\begin{align}
\P\left (Y_i =0 | S(x_i) \right) & = p_i=  \exp(-e^\xi S(x_{i}) ) \\
\E\left ( Y_i \vert Y_i >0 , S(x_i)\right)  & =  \frac{S(x_i)}{1-p_i},\\  \nonumber
\V ar( \log{Y_i}\vert Y_i >0, S(x_i) )& = \mu_i^2 (e^{\sigma^2}-1), \cr \nonumber
\end{align}

@@

The inference is realized through Template Model Builder (TMB), an effective tool to build hierarchical models and perform maximum likelihood estimation through automatic differentiation and Laplace Approximation [@kristensen_tmb_2016].

XXXX  Il faut aussi présenter la partie commercial ou dire que c'est comme dans Alglave 2022

@@

## Simulation-estimation

To evaluate the impact of reallocation on model outputs and how our alternative approach can improve model accuracy, we conduct simulation-estimation.

@@

In these two sets of simulation-estimation, the covariate is modelled as a continous GRF that we suppose known at each point of the grid. The covariate effect is fixed to $\beta_S=2$ and the intercept is also fixed to $\mu=2$. Regarding commercial data, the number of fishing pings per declaration is fixed to 10 as it is the average number of fishing locations for a single declaration in real data. All parameterizations are detailed in the Table 1.

@@

Two important variables may affect the accuracy of model outputs: the amount of commercial data and the number of fishing zones explored within one single declaration. In these simulations-estimations, we intend to explore the effect of these 2 variables.

@@

Furthermore, the samples belonging to a single declaration can be sampled in a single restricted zone or can mix catches from distinct zones (within a unique statistical rectangle). Note that we make a distinction between fishing zones and statistical rectangles: fishing zones are included in a statistical rectangle and there can be several fishing zones within a statistical rectangles. Consequently, a declaration can mix catches that have been realized in zones of high biomass and in zones of low biomass. For instance, a declaration can aggregate data from several fishing operations that occured the same day within the same statistical rectangle, but that were realized on 2 distinct types of fishing grounds (and then on two distinct habitats). Reallocating uniformly the declaration will strongly homogeneise the actual catch, will mix up information from to different grounds and then may lead to a strong loss of accuracy in model outputs. It is expected that when the number of fishing zones within a declaration increases, the accuracy of the model outputs decreases. To assess the effect of such process, we simulated the pings of a fishing declaration assuming they were either realized in a single zone, in 3 distinct zones or in 5 distinct zones.

>>>>

\begin{equation}
\label{eq:defY}
Y_i | S(x_i)  \overset{ind}{\sim} \M{p_i}{\mu_i}{\sigma^2},
\end{equation}
with $p_i \defeq \exp(-e^\xi S(x_{i})$ the proportion of the mixture, $\mu_i\defeq 
\frac{S(x_i)}{1-p_i}$ the expected catch when positive and $\sigma^2$ its variance (this parametrization of a lognormal distribution is detailed in SMXXXX and corresponds to

where $p_i\defeq \exp(-e^\xi S(x_{i}))$ is the mixture weight, $\mu_i \defeq \frac{S(x_i)}{1-p_i}$ is the mean of the lognormal distribution and $\sigma^2$ its variance, so that  
\begin{align}
\P\left (Y_i =0 | S(x_i) \right) & = p_i=  \exp(-e^\xi S(x_{i}) ) \\
\E\left ( Y_i \vert Y_i >0 , S(x_i)\right)  & =  \mu_i = \frac{S(x_i)}{1-p_i},\\  \nonumber
\V ar( Y_i\vert Y_i >0, S(x_i) )& = \mu_i^2 (e^{\sigma^2}-1), \cr \nonumber
\end{align}

@@

The inference is realized through Template Model Builder (TMB), an effective tool to build hierarchical models and perform maximum likelihood estimation through automatic differentiation and Laplace Approximation [@kristensen_tmb_2016]. We made two simplifications. We use the Stochastic Partial Differential Equations (SPDE) approach to represent the spatiel field and we use integrated Nested Lappalace approximation to compute le likelihood. The stochastic random field is also approximated by a piecewise constant process defined on a fine grid.

XXXX  Il faut aussi présenter la partie scientific ou dire que c'est comme dans Alglave 2022

@@

## Comparison of the two approaches based on a simulation study

To evaluate the impact of reallocation on model outputs and how our alternative approach can improve model accuracy, we conduct a simulation study.

@@

In these two sets of simulation studies, the covariate is modelled as a continous GRF that we suppose known at each point of the grid (when present the spatial random component is also a GRF but its values are not observed). The covariate effect is fixed to $\beta_S=2$ and the intercept is also fixed to $\mu=2$. Regarding commercial data, the number of fishing pings per declaration is fixed to 10 as it is the average number of fishing locations for a single declaration in real data. All parameterizations are detailed in the Table 1.

@@

Two important variables may affect the accuracy of model outputs: the amount of commercial data and the number of fishing zones explored within one single declaration. In these simulations, we intend to explore the effect of these 2 variables.

@@

Furthermore, the samples belonging to a single declaration can be sampled in a single restricted zone or can mix catches from distinct zones (within a unique statistical rectangle). Note that we make a distinction between fishing zones and statistical rectangles: fishing zones are included in a statistical rectangle and there can be several fishing zones within the same statistical rectangles. Consequently, a declaration can mix catches that have been realized in zones of high biomass and in zones of low biomass. For instance, a declaration can aggregate data from several fishing operations that occured the same day within the same statistical rectangle, but that were realized on 2 distinct types of fishing grounds (and then on two distinct habitats). Reallocating uniformly the declaration will strongly homogeneise the actual catch, will mix up information from to different grounds and then may lead to a strong loss of accuracy in model outputs. It is expected that when the number of fishing zones within a declaration increases, the accuracy of the model outputs decreases. To assess the effect of such process, we simulated the pings of a fishing declaration assuming they were either realized in a single zone, in 3 distinct zones or in 5 distinct zones.
